\chapter{Interviews}
\section{First meeting with Birken}
\subsection{Disposition}
\begin{itemize}
	\item Avoid boolean or leading questions.
	\item Scenarios:
		\begin{itemize}
			\item digiPECS
			\item aSchedule
			\item plAytime (displays play instructions)
		\end{itemize}
	\item How could you administrate devices/applications? Suggestions?
	\item Rich pictures/images
	\item How do you create new or better meanings in communication?
	\item Prototypes
	\item Clear usage of time.
		\begin{itemize}
			\item Right now, what do the parents do, what do you do? (Explorative)
			\item Do you regularly discuss the child and their activities? How do you communicate? (Verification)
			\item Do you make detailed scheduling? Are the children involved in this activity? (Verification)
			\item How does a usual day play out? (Explorative)
			\item How do you communicate with the children? (Explorative)
			\item Reaction on removing their items (like a phone)? (Verification)
		\end{itemize}
\end{itemize}
\subsection{Questions proper}
\begin{description}
	\item[10 mins] Introduction (names, the group, overall project goals, our intentions with the meetings)
	\item[10 mins] Introduction of the currently working GIRAF system, excluding the admin app - this is done specifically to avoid associations with that app when IT options are discussed.
	\item[5 min] Our specific goal, a PC-based administration program.
	\item[20 min] How is a typical day (or week) structured for the supervisors?
		\begin{itemize}
			\item Areas of responsibility (parents vs. supervisors)
			\item How is planning done? During the work day and how far ahead?
			\item Does the institution have access to a PC?
			\item Variation in daily activities.
			\item Is it a realistic goal to give children access to a tablet? In an estimate, how large a group of the children are functioning high enough to work with such a device?
		\end{itemize}
	\item[20 min] Communication
		\begin{itemize}
			\item Which methods of communication exist for children with autism beyond imagery/pictograms?
			\item How is a single day's schedule presented? One event at a time or a large presentation at the beginning?
			\item How are new meanings introduced to non-verbal children? For example new pictograms.
			\item Are the children involved in deciding the activities?
			\item What kind of reactions could be expected from removing an item they consider theirs?
		\end{itemize}
	\item[25 min] abstraction to IT solutions
		\begin{itemize}
			\item Debate possible IT solutiosn to ease/improve the daily work.
			\item How can It improve your working day?
			\item Optionally consider directly discussing administration solutions or work with rich pictures. Bring blank paper to draw on if possible.
		\end{itemize}
\end{description}