\section{Autism}
Autism is defined as a developmental disorder, which effect the brains ability to develop communications and social skill. Autism often appears during the first three years of a child's life, and often the disorder is diagnosed during the following years.
The definition of autistic children is broad and some autistic children may have different symptoms, while a few number of symptoms, which is common for all autistic children, is used as base for the diagnosis. The symptoms is a follow:
\begin{itemize}

  \item{Lack of communications skills.}
   \begin{itemize}
     \item{The child may have slowly or no development of language. The child can use gesture as communication instead of words, and they may have trouble with maintain focus at a conversation, or have trouble starting a conversation at all.}
   \end{itemize}
   
  \item{Lack of social skills.}
   \begin{itemize}
     \item{The child may have difficulty making friends. The child may be withdrawn, or may not respond to eyecontact and smiles. The child may treat other children or adults as objects, and may rather play alone than play with other children or adults.}
   \end{itemize}

  \item{Repetitive and/or compulsive behavior}
    \begin{itemize}
      \item{The child may have unusual distress if particular routines is changed or not being followed and may preform repeated body movements.}
    \end{itemize}
  
\end{itemize}

The exact causes of autism is still unknown, but it is meant to be a combination of different factor.%, which is the cause of the disorder. gentagelse 
Some possible causes, which has been suspected though not proven, is as follow:

\begin{itemize}
  
  \item{Diet}
  \item{Changes of the digestive tract}
  \item{Poison by mercury}
  \item{Lack of the body's ability to use vitamins and minerals properly}
  \item{Sensitivity against vaccines}
  
\end{itemize}

Even though the factors listed above is mostly physical, the autistic disorder is also meant to be linked to unusual biology and the chemistry of the brain.
It seems that genetic have some important factors. E.g. it is more likely for identical twins, than fraternal twins or siblings, to both be autistic.
