\section{Development methodology}
\todo{"vurdering på partner programming, den evalutionær/agile metode, hvordan var det at bruge prototype."}

The use of prototypes was essential to ensure that more than one perspective were taken in when designing. With the user's involvement and testing on the protoypes, time was saved when narrowing down to a system definition and choosing a focus point. Protoypes were created on blackboard, paper and in code. The blackboard prototypes helped the group visualise how changes would affect the interface and helped involving everyone within the group in designing.

To develop the product, the group split into three smaller groups, each including two individuals; that partnered up to write code and help each other while developing.
The original idea was to rotate these small groups between programming tasks, to introduce everyone to all aspects of the project and to prevent people from getting stuck.
Although the idea was good, it was not used in the end; reason beeing that development was driven in contrast with the agile method, but without purging unusable code.
This made it difficult for people to get started on other tasks, and the group later decided that each group should stick with their respective task.

The group's use of the agile method was not quite as it was intended; since some rules regarding unusable code, deadlines and testing were not respected.
Because of the difference in experience with developing within the group and lack of communication, some parts and tasks took much longer time than predicted, which resulted in tasks beeing pushed on to others.
